### 2021-12-03 manuscript.tex
Add screenshots for Wikidata Bib session [ci skip]
This build is based on
https://github.com/lubianat/quali_phd/commit/d4734c3110210b188b6c531653e9e446bd8e91b4.

This commit was created by the following CI build and job:
https://github.com/lubianat/quali_phd/commit/d4734c3110210b188b6c531653e9e446bd8e91b4/checks
https://github.com/lubianat/quali_phd/actions/runs/1535616020

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/2936776523ea1584882e2a08c3247194f8f4a1c7/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/2936776523ea1584882e2a08c3247194f8f4a1c7}{lubianat/quali\_phd@2936776}
on December 2, 2021.

>>>>

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/d4734c3110210b188b6c531653e9e446bd8e91b4/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/d4734c3110210b188b6c531653e9e446bd8e91b4}{lubianat/quali\_phd@d4734c3}
on December 3, 2021.
